BivData Setup

### 2020-05-12 src/BivData_Setup.Rmd
updating and refining the BivData setup script. goal write final xcel file

```{r setup, include=FALSE}
library(plyr)
library(lattice)
library(dplyr)
library(ggplot2)
library(reshape2)
library(raster)

@@

@@

#write the curated file
#write.table(OG.cURATE.table.mouse, "~./MLH1repo/data/CurrentCuratedDataset_21.1.20.csv", sep=",",
#            row.names = TRUE)
#write.table(OG.cURATE.table.category, "~./MLH1repo/data/CurrentCuratedDataset_cat_21.1.20.csv", sep=",",
#            row.names = TRUE)
```

@@

@@

```{r neg.IFD, echo=FALSE}

@@

#mice to remove from the Curated_BivData -- should be similar to the mice exclude from the MLH1

@@

@@

@@

```{r Q1Q2.mouse.table, echo=FALSE}

#How Do I apply quality score things to BivData?
#make the same table but

>>>>

```{r BivData.setup, include=FALSE}
library(plyr)
library(lattice)
library(dplyr)
library(ggplot2)
library(reshape2)
library(raster)

@@

#add_mouse ect.

@@

#write the curated file
#write.table(OG.cURATE.table.mouse, "~./MLH1repo/data/CurrentCuratedDataset_21.1.20.csv", sep=",",
#            row.names = TRUE)
#write.table(OG.cURATE.table.category, "~./MLH1repo/data/CurrentCuratedDataset_cat_21.1.20.csv", sep=",",
#            row.names = TRUE)

@@

#write.xlsx2(MLH1.merge.Skel, "Total.SC_merge.MLH1.xlsx", sheetName = "Sheet1", 
#            col.names = TRUE, row.names = FALSE, append = FALSE)

@@

```{r neg.IFD, echo=FALSE, eval=FALSE}

@@

#mice to remove from the Curated_BivData -- should be similar to the mice exclude from the MLH1 (why?)

@@

after all of these chunks are run, save the excel file for Curated_BivData

DUPs, negative IFDs, remove juvi and MLH1 exclude mice,

There are 3 bivalents with Per.Foci2 > 1 (remove or go correct)

```{r write.total.SC, echo=FALSE}

#write.xlsx2(MLH1.merge.Skel, "Total.SC_merge.MLH1.xlsx", sheetName = "Sheet1", 
#            col.names = TRUE, row.names = FALSE, append = FALSE)

@@

)
#can I plot these stats
```

@@
